### 2017-08-16 Paper01_EnthalpyAndCrystallization.tex
Results - Xtal Enthalpy - added new paragraph. draft done

The deconvolution fits were integrated to find the area under each curves. This information provides the \gls{h} of the crystallisation formation of each phase. This is presented in Tables \ref{tab:Bulk_Enthalpy} and \ref{tab:Film_Enthalpy} for the bulk and film respectively. Figure \ref{fig:DSC_Decon} shows the \Tx~ onsets and \acrfull{h} for both the bulk and film plotted together.

>>>>

The deconvolution fits were integrated to find the area under each curve. This information provides the \gls{h} of the crystallisation formation of each phase. These energies are presented in Tables \ref{tab:Bulk_Enthalpy} and \ref{tab:Film_Enthalpy} for the bulk and film respectively. Figure \ref{fig:DSC_Decon} shows the \Tx~ onsets and \acrfull{h} for both the bulk and film plotted together.

From Tables \ref{tab:Bulk_Enthalpy} and \ref{tab:Film_Enthalpy}, and Figure \ref{fig:DSC_Decon} it can be seen most of the crystallisation formation energy is needed to form the $1^{st}$, $3^{rd}$, and $5^{th}$ phases (i.e. \Tx $_{1, 3, 5}$). With these three phases accounting for approximately $73 \pm 7\%$ of the bulk crystallisation. The combined crystallisation energy of these three bulk phases is also similar to the total energy for the films. Demonstrating that the bulk requires more energy to crystallize than the films. 
\todo{This is what ISMANAM scientist said would be expected from a not USG glass. i.e. this is the typical expectation [sources needs].}
